Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?

### 2022-07-05 README.Rmd
update

```{r zip_dtc, fig.height = 8,fig.width=8}
#scatter plot
zip %>% 
  #filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
  ggplot(aes(y = daytoclose_diff, x = rate*100, size = daytoclose_2019, col = ZIP))+
  geom_point()+
  geom_smooth(method=lm)+
  facet_wrap(~CATEGORY, scale = "free_y")+
  labs(y = "Change in Response Time",x = "COVID-19 infection rate")+
  theme_bw()+
  theme(legend.position = "none")
```

@@

@@

```{r tab2}
#ols 
reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Health",], DAYTOCLOSE~did + rate + after))
#fe: rate + after
reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|rate+after ))
#fe: rate + date(year-month)
reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|rate+factor(date) ))

>>>>

```{r zip_dtc, fig.height = 3,fig.width=8}
#scatter plot
zip %>% 
  left_join(diff) %>%
  filter(CATEGORY %in% c("Public Safety","Public Health","Parks & Recreation")) %>%
  ggplot(aes(y = daytoclose_diff, x = rate*100, size = daytoclose_2019, col = ZIP))+
  geom_point()+
  geom_smooth(method=lm)+
  facet_wrap(~reorder(CATEGORY,-diff_pchg), scale = "free_y")+
  labs(y = "Change in Response Time",x = "COVID-19 infection rate")+
  theme_bw()+
  theme(legend.position = "none")
```

@@

#combine reg 
screenreg(list(reg_ols, reg_fe_a, reg_fe_b), 
          omit.coef = "after|rate|Intercept", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("OLS", "FE period-rate", "FE date-rate"),
          custom.coef.names = "DiD effect"#,
        #file = "reg.doc"
          )

@@

```{r tab2}
#ols 
reg_ols = (lm(data= dat_reg[dat_reg$CATEGORY == "Public Health",], DAYTOCLOSE~did + rate + after))
#fe: rate + after
reg_fe_a = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|rate+after ))
#fe: rate + date(year-month)
reg_fe_b = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|rate+factor(date) ))
#fe: nbh + date(year-month)
#reg_fe_c = (felm(data = dat_reg[dat_reg$CATEGORY == "Public Health",],DAYTOCLOSE~did|factor(NEIGH)+factor(date) ))
